### 2015-08-14 writing/SNLI paper/entailment_eval.tex
Fix bolding
Train numbers on SICK

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{SNLI} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}            & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}               & \b{72.2} & \b{71.4} & \t{61.5} \\
\t{Classifier + Lexical Resources} & \b{--}   & \b{78.8} & \t{63.6} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\  % broken! At least, on SNLI...
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class test accuracy for two simple baseline systems included in the
  Excitement Open Platform, as well as SICK and RTE results for
  a model making use of more sophisticated lexical resources.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\hspace{-1.2em}\b{SNLI}} & \b{SICK}\\
 & \t{Train} & \t{Test} & \t{Test}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \b{77.3} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} & \t{74.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} & \t{69.4}\\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy, training on either our data or SICK, including models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}). For the model trained on SNLI, we report results both on the test set and the training set to judge overfitting.
}
\end{table}
%
% END BOW RESULTS TABLE
%

>>>>

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{SNLI} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}            & \t{71.9} & \t{65.4} & \t{61.9} \\
\t{Classifier Based}               & \b{72.2} & \t{71.4} & \t{61.5} \\
\t{Classifier + Lexical Resources} & \t{--}   & \b{78.8} & \b{63.6} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\  % broken! At least, on SNLI...
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class test accuracy for two simple baseline systems included in the
  Excitement Open Platform, as well as SICK and RTE results for
  a model making use of more sophisticated lexical resources.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\hspace{-1.2em}\b{SNLI}} & \multicolumn{2}{c}{\b{SICK}}\\
 & \t{Train} & \t{Test} & \t{Train} & \t{Test}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \t{90.4} & \b{77.8} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6}  & \t{88.1} & \t{77.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4}  & \t{69.9} & \t{69.6} \\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy, training on either our data or SICK, including models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
We report results both on the test set and the training set to judge overfitting.
}
\end{table}
%
% END BOW RESULTS TABLE
%
